---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)

devtools::load_all()
```

# jpw

<!-- badges: start -->
<!-- badges: end -->

Personal R package to house miscellaneous tidbits of code. 

## Installation

You can install the development version of jpw from [GitHub](https://github.com/) with:

```{r, eval = FALSE}
install.packages("devtools")
devtools::install_github("WhiteJP/jpw")

```

And load it: 

```{r eval = FALSE}
library(jpw)
```

## Examples

Below are some examples of functions in jpw.

* put vectors in prose format

```{r examples}
vec2prose(c("Peanut", "Butter", "Jelly"), oxford_comma = FALSE)
```

* evaluate logical expressions where NAs proliferate. NA in any part of input 
-> NA in output.

```{r}
x <- c(1,  2, 3, NA,  5, NA, 7,  8, NA, 10)
y <- c(NA, 9, 8,  7,  5, NA, 4,  3,  2,  1)

na2na(x > 8 | x == y)

```

* left and right censor data

```{r}
censor_left(1:10, min = 5)
censor_right(1:10, max = 5)
censor_both(1:10, min = 3, max = 7)
```

* Extract or remove numbers from strings

```{r}
extract_nums_tgthr(c("sdff234", "12aaa34"))
extract_nums_all(c("12aaa34", "-12.4 54.3", "adfsdf.344 -1.2 4"))
remove_nums(c("12aaa34",  "adfsdf.344 -1.2 4"), trimws = TRUE)

```

* scale vectors to have a specified min and max

```{r}
normalise(1:10) # min = 0 max = 1
scale_minmax(1:10, mn = -100, mx = 100) # min = `mn`, max = `mx`

```

* convert decimal integer to binary string

```{r}
int2bin(c(12, 5, NA, 90342))
```

* add trailing zeros to integer or string

```{r}
x <- c(100010, 234,  1, 34)
add_zeros(x) # default to longest nchar in vector
add_zeros(x, len = 9) # can stipulate longer
```

* add new element to vector by index position

```{r}
add_by_position(LETTERS[1:6], "NEW", 5)
```

* get matrix with reverse diagnoal

```{r}
rev_diag(3)
rev_diag(6, x = 12)
```

* add brackets

```{r}
brackets(123)
brackets("foo", type = "square")
```

* recursively search environments to find where function defined

```{r}
where(sum)
where("sd")
```

